Kyoto VR MQP Paper First Draft

### 2019-09-09 paper.tex
got rid of euro TODO
added testing section with figures

// TODO: Need a way to add Euro character to document; the way they are in now doesn't work

@@

From all of this information, Wikitude certainly sounds like a fantastic AR development
platform; it certainly did to us. But the issue we ran into was the cost. Wikitude is, in
fact, free for eligible startups, but given the criteria they list on their site, we were not
confident that we would qualify. Aside from this option, Wikitude offers a 30-day demo
license for \euro{499}, which is a lot for use to pay for a license that would not even last for
our entire project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for their
SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget
of \$0, we knew that we would have to pass on Wikitude and choose a different AR
development platform.

@@

See Figure~\ref{fig:turtleBurger} for more details.

>>>>

@@

From all of this information, Wikitude certainly sounds like a fantastic AR development
platform; it certainly did to us. But the issue we ran into was the cost. Wikitude is, in
fact, free for eligible startups, but given the criteria they list on their site, we were not
confident that we would qualify. Aside from this option, Wikitude offers a 30-day demo
license for \euro{499}, which is a lot for use to pay for a license that would not even last for
our entire project. They also charge \euro{1990} for their SDK Pro, and \euro{2490} for their
SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget,
we knew that we would have to pass on Wikitude and choose a different AR
development platform.

@@

Our first day of on-site testing with the app took place on September 6th.
Using Editour, we rebuilt the izi.TRAVEL audio tour that Atticus already
created. The first version of the rebuilt tour had regions that were relatively
small; some regions were only a few meters across. This version of the tour can
be seen in Figure~\ref{fig:kinkakujiTour}.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
	\caption[The original version of the Kinkakuji tour]{The original version of
    the Kinkakuji tour with small regions}
	\label{fig:kinkakujiTour}
\end{figure}

Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji} to
create a second, ``chunkier'' tour.  In the tour-file \texttt{kinkakuji-chunkier},
we expanded all of the regions to accomodate for potential GPS inaccuracies
that could place the user outside the range of the audio-trigger region.
Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour that we used for field
testing at Kinkakuji.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
	\caption[The ``chunkier'' version of the Kinkakuji tour]{The ``chunkier'' version of
    the Kinkakuji tour with larger regions}
	\label{fig:kinkakujiChunkierTour}
\end{figure}

We tested using two phones at the same time: an iPhone 8 and a Samsung Galaxy
S7. The iPhone 8 is newer, more powerful and therefore more suited for use with
AR. We primarily used this phone to test the AR features of the app. Even
though the Samsung Galaxy had difficulty with basic AR features such as
ground-plane detection, it was still capable of triggering the audio track
based on GPS position.

Our previous testing involved creating a ``mock tour'' on the Ritsumeikan campus.
While this let us know generally which features of the app were working, it was
very difficult to know how ahead of time how well our app would work at Kinkakuji.

We were surprised by how intuitively each region triggered on the first try.
With a few exceptions, the audio started when the subject of the audio track
was in view. During our first walkthrough of Kinkakuji, we triggered every
region and audio track but one. The region that we missed on the first pass,
``Final Viewpoint'', requires the user to take a right at a fork in the road
instead of continuing along the main path. This is not necessarily a problem
with the design of the regions; instruction provided by the audio tour could
remedy this, directing the user toward the viewpoint that is off of the main
path.

Initially, we loaded the app onto the Samsung Galaxy S7 as a backup, since the
app is not fully functional on a phone that old. At the same time, it was
informative to take both phones through the tour. Initially, we made the design
decision to update the GPS location every 60 frames. On a phone running the app
at full speed, this should happen once every second. Because the Samsung Galaxy
S7 was having trouble running the app at full speed, the GPS updated far less
frequently. This was an oversight that would have been difficult to catch if we
had not tested on hardware below the recommended specifications.

Other bugs resulted from oversights that were difficult to catch with our
on-campus testing.  For example, we noticed that we forgot to back-up the audio
slider when entering a new region.  Because of this, when we entered a new
region when the audio slider was past the endpoint of the new audio track, the
audio would not play. For example, if the previous audio track were a minute
long, and if the second track were only thirty seconds long, the app would try
to play a thirty second audio track from the one minute mark. Since we were
running the app on phones, we could not easily see when errors were thrown.
Similarly, if the user were to enter a new region while thirty seconds into the
previous audio track, the new audio track would start at the thirty second
mark. During our on-campus testing, we were using songs rather than narration.
Since the songs were relatively long and not always obvious when they started
partway through, we did not catch this until we got out to Kinkakuji.  Luckily,
this was trivial to fix.
